---
title: "table for docx"
author: "NT"
date: "1/16/2018"
output: word_document
---

---
title: "change text style in a table"
author: "NT"
date: "1/9/2018"
output:
  pdf_document: default
---

This is a kable example.
Row group titles are added

```{r library}
library(knitr)
library(kableExtra)
library(magick)

```

When export a table to docx, it is always troublesome. The best way seems to make an vector image, then load the image to visualize.
So, here a table is exported to pdf, then import the pdf as an image.

##import test data
Motor Trend Car Road Tests in datasets package is loaded.
```{r import data}

dt <- mtcars[1:5, 1:4]
##https://github.com/haozhu233/kableExtra
```

## Example Table

###Latex
```{r LaTeX Table 1}
#from an official example
kable(dt, format = "latex", booktabs = T, caption = "Demo Table") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F) %>%
  add_header_above(c(" ", "Group 1" = 2, "Group 2[note]" = 2)) %>%
  add_footnote(c("table footnote"))
```

##Export the table as a pdf
###Latex
```{r export as pdf}
# LaTeX Table
path <-  kable(dt, format = "latex", booktabs = T, caption = "\\em{Demo} \\textnormal{Table}", escape =FALSE) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F) %>%
  add_header_above(c(" ", "Group 1" = 2, "Group 2[note]" = 2)) %>%
  add_footnote(c("\\textsc{table} \\textbf{footnote}"), escape=FALSE)  %>% 
  kable_as_image(keep_pdf = T)
    
  include_graphics(path[1])


```


```{r}

tbl <- kable(dt, format = "latex", booktabs = T, caption = "\\em{Demo} \\textnormal{Table}", escape =FALSE) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F) %>%
  add_header_above(c(" ", "Group 1" = 2, "Group 2[note]" = 2)) %>%
  add_footnote(c("\\textsc{table} \\textbf{footnote}"), escape=FALSE)

 if(out_type != "docx"){
    tbl 
  } else {
  path <-  tbl  %>% 
  kable_as_image(keep_pdf = T)
    
  include_graphics(path[1])
  }
```

