---
title: "R stack calculation test"
author: "naru-T"
output:
  html_document: default
  html_notebook: default
---

### Test raster stack calculation. 
just try to set NA values when less than 0.5 in raster stack
check the processing time .

* set up raster stack
```{r}
library(raster)
r <- raster(ncols=3000, nrows=3000)
r1 <- setValues(r, runif(ncell(r)))
r2 <- setValues(r, runif(ncell(r)))
r3 <- setValues(r, runif(ncell(r)))
r4 <- setValues(r, runif(ncell(r)))
r5 <- setValues(r, runif(ncell(r)))
r6 <- setValues(r, runif(ncell(r)))
stk <- stack(r1,r2,r3,r4,r5,r6)

```

* try normal approach
this approach depends on RAM. 
it is only faster when using smaller raster data. 
Do not try this way if you use big raster data.
```{r}
system.time(stk[stk <= 0.5 ] <- NA)
summary(stk)
```

   user  system elapsed   
  0.984   0.406   1.403 
  
  
  

* try user-defined function approach


this does not necessary to prepare large amount of RAM.
```{r}
  na_func <- function(x){
    x[x <= 0.5] <- NA
    return(as.vector(x))
  }

stk <- stack(r1,r2,r3,r4,r5,r6)
system.time(ans <- calc(stk, na_func))
summary(ans)
```
 user  system elapsed     
 10.585   0.254  10.898 
 
 
 
#### calculation for temporal interpolating NA values in raster stack. 


very nice function by https://stat.ethz.ch/pipermail/r-sig-geo/2010-December/010216.html    
It is always a good way to use calc function, especially when using big raster data.
this do not depend on big RAM space.

```{r}
require(zoo)


fill.NA <- function(x,na.rm = F){
 #x[x==0] <- NA
 if(length(which(is.na(x)==F))>2){
 fill <- approxfun(x, y=NULL, method='linear', rule=2)
 rec <- which(is.na(x))
 x[rec] <- fill(rec)
 }
 
 return(x)
}

stk_fillNA <- calc(stk, fun=fill.NA)

summary(stk_fillNA)

```

